---
title: "Week 3 Assignment"
author: "Milena Stevanovic"
date: "10 November 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

## ToothGrowth analysis

- We want to analyze the ToothGrowth data in the R datasets package.

- The goal is to compare tooth growth by supplemment and dose.

- We will use basic exploratory data analyses.

## Effect of Dosage by Supplement Type

```{r, message=FALSE, warning=FALSE}
library("plotly")
data(ToothGrowth)
colnames(ToothGrowth)<-c("Length", "Supplement", "Dose")
ToothGrowth$Dose<-as.factor(ToothGrowth$Dose)
plot_ly(ToothGrowth, x = ~Supplement, y = ~Length, color = ~Dose, type = "box", boxpoints = "all", jitter = 0.2, pointpos = -1.2) %>% layout(boxmode = "group")
```

## Effect of Supplement Type by Dosage

```{r, message=FALSE, warning=FALSE}
library("plotly")
data(ToothGrowth)
colnames(ToothGrowth)<-c("Length", "Supplement", "Dose")
ToothGrowth$Dose<-as.factor(ToothGrowth$Dose)
plot_ly(ToothGrowth, x = ~Dose, y = ~Length, color = ~Supplement, type = "box", boxpoints = "all", jitter = 0.2, pointpos = -1.2) %>% layout(boxmode = "group")
```

## Conclusions

Final conclusions from this analysis are:

- Increasing the dose level leads to increased tooth growth.

- Supplemment OJ leads to increased tooth growth comparing to supplemment VC when dose is 0.5 or 1. But, when dose is 2, it is uncertain whether there will be a greater effect from either OJ or VC.